### 2020-03-23 Strings2020/strings1/strings1.tex
Finalize strings2, update advqft2

	\begin{enumerate}
	\item Under special conformal transformation $K(a)$, metric $\delta_{\mu\nu}\mapsto g_{\mu\nu}$ while:
	\begin{equation}
		g_{\alpha\beta}
			\dd{\tilde{x}^\alpha}
			\dd{\tilde{x}^\beta}
		= \delta_{\mu\nu}
			\dd{x^\mu}
			\dd{x^\nu},\quad
		g_{\alpha\beta}
		= \delta_{\mu\nu}
			\pdv{x^\mu}{\tilde{x}^\alpha}
			\pdv{x^\nu}{\tilde{x}^\beta}
		\label{eq:metric_transform}
	\end{equation}
	To calculate this we have to know the inverse transformation $x = K^{-1}(a)\,\tilde{x}$. First, notice the following decomposition\footnote{
		See \textit{Di Francesco et al}, and also \https{github.com/davidsd/ph229}. 
	} of $K(a)$:
	\begin{equation}
		\tilde{x}^\mu
		= \frac{\frac{x^\mu}{x^2} + a^\mu}{
			\frac{1}{x^2}
			+ \frac{2a\cdot x}{x^2} + a^2
		}
		= \frac{\frac{x^\mu}{x^2} + a^\mu}{
			\abs{\frac{x^\mu}{x^2} + a^\mu}^2
		},\\[1ex]
		\text{i.e.}\quad
		K(a)\colon\ %
			x^\mu
			\ \xmapsto{\ I\ }\ %
			\frac{x^\mu}{x^2}
			\ \xmapsto{\ T(a)\ }\ %
			y^\mu = \frac{x^\mu}{x^2} + a^\mu
			\ \xmapsto{\ I\ }\ %
			\tilde{x}^\mu
			= \frac{y^\mu}{y^2},
		\label{eq:special_conformal_decomp} \\[.5ex]
		\text{i.e.}\quad
		\frac{\tilde{x}^\mu}{\tilde{x}^2}
			= \flatfrac{
				\frac{y^\mu}{y^2}
			}{
				\frac{1}{y^2}
			}
			= y^\mu = \frac{x^\mu}{x^2} + a^\mu
		\label{eq:special_conformal_simplified}
	\end{equation}

	From \eqref{eq:special_conformal_simplified}, we see that the transformation parameter $a^\mu$ composes linearly: $K(b)\,K(a) = K(a+b)$, therefore $K^{-1}(a) = K(-a)$, and we have:
	\begin{equation}
		x^\mu = K(-a)\,\tilde{x}^\mu
		= \frac{\tilde{x}^\mu - \tilde{x}^2 a^\mu}{
			1 - 2a\cdot \tilde{x} + a^2 \tilde{x}^2
		}
		= \frac{\tilde{y}^\mu}{y^2},\\[1.5ex]
	\begin{aligned}
		\pdv{x^\mu}{\tilde{x}^\alpha}
		&= \pdv{x^\mu}{\tilde{y}^\sigma}
			\pdv{\tilde{y}^\sigma}{\tilde{x}^\alpha}
		= \pqty{
			\pdv{\tilde{y}^\sigma}
			\frac{\tilde{y}^\mu}{\tilde{y}^2}
		} \pdv{\tilde{x}^\alpha} \pqty{
			\frac{\tilde{x}^\sigma}{\tilde{x}^2}
			- a^\sigma\!
		}
		= \pqty{
			\pdv{\tilde{y}^\sigma}
			\frac{\tilde{y}^\mu}{\tilde{y}^2}
		} \pqty{
			\pdv{\tilde{x}^\alpha}
			\frac{\tilde{x}^\sigma}{\tilde{x}^2}
		} \\[1ex]
		&= \pqty{
			\tilde{y}^2\delta^\mu_\sigma
			- 2\tilde{y}^\mu \tilde{y}_\sigma
		} \pqty{
			\tilde{x}^2\delta^\sigma_\alpha
			- 2\tilde{x}^\sigma \tilde{x}_\alpha
		} \Big/ \pqty{\tilde{y}^4 \tilde{x}^4},
	\end{aligned}\\[1ex]
	\begin{aligned}
		g_{\alpha\beta}
		&\xlongequal{\eqref{eq:metric_transform}}
		\delta_{\mu\nu} \pqty{
			\tilde{y}^2\delta^\mu_\sigma
			- 2\tilde{y}^\mu \tilde{y}_\sigma
		} \pqty{
			\tilde{x}^2\delta^\sigma_\alpha
			- 2\tilde{x}^\sigma \tilde{x}_\alpha
		} \pqty{
			\tilde{y}^2\delta^\nu_\rho
			- 2\tilde{y}^\nu \tilde{y}_\rho
		} \pqty\big{
			\tilde{x}^2\delta^\rho_\beta
			- 2\tilde{x}^\rho \tilde{x}_\beta
		} \Big/ \pqty{\tilde{y}^8 \tilde{x}^8}\\
		&\xlongequal{\sum_{\mu,\nu}}
		\tilde{y}^{-4} \delta_{\sigma\rho} \pqty{
			\tilde{x}^2\delta^\sigma_\alpha
			- 2\tilde{x}^\sigma \tilde{x}_\alpha
		} \pqty\big{
			\tilde{x}^2\delta^\rho_\beta
			- 2\tilde{x}^\rho \tilde{x}_\beta
		} \Big/ \tilde{x}^8 \\
		&\xlongequal{\sum_{\sigma,\rho}}
			\tilde{y}^{-4} \tilde{x}^{-4}
			\delta_{\alpha\beta}
	\end{aligned}
	\end{equation}
	We see that $g_{\alpha\beta} = f(x)\,\delta_{\alpha\beta}$, with coefficient:
	\begin{equation}
		f(x) = \tilde{y}^{-4} \tilde{x}^{-4}
		\xlongequal{%
			\eqref{eq:special_conformal_decomp}%
		} \frac{x^4}{\tilde{x}^4}
		\xlongequal{%
			\eqref{eq:special_conformal_simplified}%
		} \pqty{
			1 + 2a\cdot x + a^2 x^2
		}^2
	\end{equation}
	\qed[(a)]
	\vspace*{-1\baselineskip}

@@

	In 2D, we have $\mu = z,\bar{z}$; for $\phi(z,\bar{z})$ with conformal weight $(h,\bar{h})$, consider $
		z\mapsto z',\,
		\bar{z}\mapsto \bar{z}'
	$. For convenience, let's first consider a generic variation $\var{z} = \epsilon(z,\bar{z})$ before restricting to spacetime translation; we have:
	\begin{equation}
		\phi'(z',\bar{z}')
		= \pqty\Big{\dv{z'}{z}}^{\!\! -h}
			\pqty\Big{\dv{\bar{z}'}{\bar{z}}}^{
				\!\! -\bar{h}
			}
			\phi(z,\bar{z}),\\[1ex]
		\tilde{\delta}\phi
		= \pqty{
			- h\,\pd\epsilon
			- \bar{h}\,\pdbar\bar{\epsilon}\,
		}\,\phi,\\
		\var{\phi} 
		= \tilde{\delta}\phi
			-\pdv{\phi}{x^\mu} \var{x^\mu}
		= \pqty{
			- h\,\pd\epsilon
			- \bar{h}\,\pdbar\bar{\epsilon}\,
		}\,\phi
			- \epsilon\,\pd\phi
			- \bar{\epsilon}\,\pdbar\phi,
		\label{eq:var_field_compact_supp}
	\end{equation}
	Here we use $\tilde{\delta}\phi$ to denote the ``internal'' variation related to the conformal weights.

	Note that $\phi = b,c$ are anti-commuting Grassmann numbers, variation of the action gives:
	\begin{equation}
	\begin{aligned}
		\var{S}[b,c,\var{b},\var{c}]
		&= \frac{1}{2\pi} \int \dd[2]{z} \pqty{
			\var{b}\,\pdbar c
			+ b\,\pdbar \var{c}
		} \\
		&= \frac{1}{2\pi} \int \dd[2]{z} \pqty{
			- \pdbar c\,\var{b}
			- \pdbar b\,\var{c}
		} + \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar \pqty{b\var{c}}
	\end{aligned}
	\label{eq:bc_action_var}
	\end{equation}
	For \textit{unknown} $b,c$ and {arbitary} $\var{b},\var{c}$, the second term is reduced to a boundary term at infinity and can be dropped; imposing $\var{S} = 0$ gives the equation of motion (EOM): $\pdbar b = \pdbar c = 0$.

	On the other hand, for \textit{on-shell} $b,c$ and compactly supported $\varphi = \var{b},\var{c}$ given in \eqref{eq:var_field_compact_supp}, the first term in \eqref{eq:bc_action_var} vanishes while $\var{S}_0 = 0$ still holds; this gives:
	\begin{equation}
	\begin{aligned}
		0 = \var{S}_0
		&= \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar \pqty{b\var{c}}
		= \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar\,\pqty\big{
				- (1-\lambda)\,bc\,\pd\epsilon
				- b\,\pd c\,\epsilon
			} \\
		&= \frac{1}{2\pi} \int \dd[2]{z}
			\pqty\big{
				- (1-\lambda)\,bc\,
					\pdbar\pd\epsilon
				- b\,\pd c\,\pdbar\epsilon
			}
	\end{aligned}
	\end{equation}
	Here we've distributed the $\pdbar$ operator and dropped all terms that vanish automatically by EOM. Next we shall collect the $\pd\epsilon,\pdbar\epsilon$ terms; integrating by parts on the first integrand gives:
	\begin{equation}
	\begin{aligned}
		0 = \var{S}_0
		&= \frac{1}{2\pi} \int \dd[2]{z}
			\pqty\big{
				(1-\lambda)\,\pd(bc)\,
				- b\,\pd c
			}\,\pdbar\epsilon \\
		&= \frac{1}{2\pi} \int \dd[2]{z}
			\pqty\big{
				(\pd b)\,c
				- \lambda\,\pd(bc)
			}\,\pdbar\epsilon \\
		&= - \frac{1}{2\pi} \int \dd[2]{z}
			\epsilon(z,\bar{z})\,\pd_{\bar{z}}
			\pqty\big{
				(\pd b)\,c
				- \lambda\,\pd(bc)
			}
	\end{aligned}
	\label{eq:conserved_current}
	\end{equation}

@@

	To compute $TT$ OPE, we need the OPE of $b(z)\,c(0)$; this is obtained by examining the following path integral, which is zero since the integrand is a total functional derivative:
	\begin{equation}
		0 = \int \mscr{D}b\,\mscr{D}c\,
			\fdv{\phi}\pqty{e^{-S}\,\psi}
	\end{equation}
	Taking $\phi,\psi=b,c$, this generates operator equations such as $
		\pdbar b(z)\,c(0)
		= 2\pi\delta^2(z,\bar{z})
	$. Note that $
		\pdbar(\frac{1}{z})
		= 2\pi\delta^2(z,\bar{z})
	$, which gives:
	\begin{equation}
		b(z)\,c(0) \sim c(z)\,b(0)
		\sim \frac{1}{z},\quad
		b(z)\,b(0) \sim 0
		\sim c(z)\,c(0)
	\end{equation}

@@

	\item[(b)(c)] Combining two $\psi$ expansions gives the mode expansion of $
		J\id{_i^j}
		= \normorder{\psi_i(z)\,\psi^j(z)}
	$, namely:
	\begin{equation}
		J\id{_i^j}(z)
		= \sum_{k\in\mbb{Z}}
			\frac{(J\id{_i^j})_k}{z^{k+1}},\quad
		(J\id{_i^j})_k
		= \sum_{q\in\mbb{Z}+\frac{1}{2}}
			\normorder{
				b_{iq}\,b^{j\dagger}_{k-q}
			}
	\end{equation}
	It is in fact more convenient to obtain the $JJ$ OPE first, and then use it to find the  $[J_0,J_0]$ mode commutator\footnote{
		I would like to thank \textit{谷夏} for providing this hint. 
	}; note that $
		{
			{\psi}_i(z)\,{\psi}^j(w)
		}
	$ contraction gives $\frac{\delta^j_i}{z-w}$, we have:
	\begin{equation}
		J\id{_i^j}(z)\,J\id{_k^l}(0)
		\sim \frac{
			\delta_i^l\delta_k^j
		}{z^2} + \frac{
			\delta^j_k J\id{_i^l}(0)
			- \delta^l_i J\id{_k^j}(0)
		}{z},\\[1ex]
		\bqty{
			(J\id{_i^j})_0, (J\id{_k^l})_0
		}
		= \frac{1}{(2\pi i)^2}
			\oint_0 \dd{w}
			\oint_w \dd{z}
				J\id{_i^j}(z)\,J\id{_k^l}(w)
		= \delta_i^l\,(J\id{_k^j})_0
			- \delta_k^j\,(J\id{_i^l})_0
	\end{equation}

@@

	Similar holds for $J_{ij} = \normorder{\psi_i\psi_j}$ and its OPE, but we no longer need to distinguish upper/lower indices; we have:
	\begin{equation}
		J_{ij}(z)\,J_{kl}(0)
		\sim \frac{
			- \delta_{ik}\delta_{jl}
			+ \delta_{il}\delta_{jk}
		}{z^2} + \frac{
			- \delta_{ik} J_{jl}(0)
			+ \delta_{il} J_{jk}(0)
			+ \delta_{jk} J_{il}(0)
			- \delta_{jl} J_{ik}(0)
		}{z}\\[1ex]
		\bqty{
			(J_{ij})_0, (J_{kl})_0
		}
		= - \delta_{ik} (J_{jl})_0
			+ \delta_{il} (J_{jk})_0
			+ \delta_{jk} (J_{il})_0
			- \delta_{jl} (J_{ik})_0
	\end{equation}
	This is precisely the $\mfrak{o}(n)$ algebra. 
	\qedfull

>>>>

	\begin{enumerate}
	\item Under special conformal transformation $K(a)$, metric $\delta_{\mu\nu}\mapsto g_{\mu\nu}$ while:
	\begin{equation}
		g_{\alpha\beta}
			\dd{\tilde{x}^\alpha}
			\dd{\tilde{x}^\beta}
		= \delta_{\mu\nu}
			\dd{x^\mu}
			\dd{x^\nu},\quad
		g_{\alpha\beta}
		= \delta_{\mu\nu}
			\pdv{x^\mu}{\tilde{x}^\alpha}
			\pdv{x^\nu}{\tilde{x}^\beta}
		\label{eq:metric_transform}
	\end{equation}
	To calculate this we have to know the inverse transformation $x = K^{-1}(a)\,\tilde{x}$. First, notice the following decomposition\footnote{
		See \textit{Di Francesco et al}, and also \https{github.com/davidsd/ph229}. 
	} of $K(a)$:
	\begin{gather}
		\tilde{x}^\mu
		= \frac{\frac{x^\mu}{x^2} + a^\mu}{
			\frac{1}{x^2}
			+ \frac{2a\cdot x}{x^2} + a^2
		}
		= \frac{\frac{x^\mu}{x^2} + a^\mu}{
			\abs{\frac{x^\mu}{x^2} + a^\mu}^2
		},\\[1ex]
		\text{i.e.}\quad
		K(a)\colon\ %
			x^\mu
			\ \xmapsto{\ I\ }\ %
			\frac{x^\mu}{x^2}
			\ \xmapsto{\ T(a)\ }\ %
			y^\mu = \frac{x^\mu}{x^2} + a^\mu
			\ \xmapsto{\ I\ }\ %
			\tilde{x}^\mu
			= \frac{y^\mu}{y^2},
		\label{eq:special_conformal_decomp} \\[.5ex]
		\text{i.e.}\quad
		\frac{\tilde{x}^\mu}{\tilde{x}^2}
			= \flatfrac{
				\frac{y^\mu}{y^2}
			}{
				\frac{1}{y^2}
			}
			= y^\mu = \frac{x^\mu}{x^2} + a^\mu
		\label{eq:special_conformal_simplified}
	\end{gather}

	From \eqref{eq:special_conformal_simplified}, we see that the transformation parameter $a^\mu$ composes linearly: $K(b)\,K(a) = K(a+b)$, therefore $K^{-1}(a) = K(-a)$, and we have:
	\begin{gather}
		x^\mu = K(-a)\,\tilde{x}^\mu
		= \frac{\tilde{x}^\mu - \tilde{x}^2 a^\mu}{
			1 - 2a\cdot \tilde{x} + a^2 \tilde{x}^2
		}
		= \frac{\tilde{y}^\mu}{y^2},\\[1.5ex]
	\begin{aligned}
		\pdv{x^\mu}{\tilde{x}^\alpha}
		&= \pdv{x^\mu}{\tilde{y}^\sigma}
			\pdv{\tilde{y}^\sigma}{\tilde{x}^\alpha}
		= \pqty{
			\pdv{\tilde{y}^\sigma}
			\frac{\tilde{y}^\mu}{\tilde{y}^2}
		} \pdv{\tilde{x}^\alpha} \pqty{
			\frac{\tilde{x}^\sigma}{\tilde{x}^2}
			- a^\sigma\!
		}
		= \pqty{
			\pdv{\tilde{y}^\sigma}
			\frac{\tilde{y}^\mu}{\tilde{y}^2}
		} \pqty{
			\pdv{\tilde{x}^\alpha}
			\frac{\tilde{x}^\sigma}{\tilde{x}^2}
		} \\[1ex]
		&= \pqty{
			\tilde{y}^2\delta^\mu_\sigma
			- 2\tilde{y}^\mu \tilde{y}_\sigma
		} \pqty{
			\tilde{x}^2\delta^\sigma_\alpha
			- 2\tilde{x}^\sigma \tilde{x}_\alpha
		} \Big/ \pqty{\tilde{y}^4 \tilde{x}^4},
	\end{aligned}\\[1ex]
	\begin{aligned}
		g_{\alpha\beta}
		&\xlongequal{\eqref{eq:metric_transform}}
		\delta_{\mu\nu} \pqty{
			\tilde{y}^2\delta^\mu_\sigma
			- 2\tilde{y}^\mu \tilde{y}_\sigma
		} \pqty{
			\tilde{x}^2\delta^\sigma_\alpha
			- 2\tilde{x}^\sigma \tilde{x}_\alpha
		} \pqty{
			\tilde{y}^2\delta^\nu_\rho
			- 2\tilde{y}^\nu \tilde{y}_\rho
		} \pqty\big{
			\tilde{x}^2\delta^\rho_\beta
			- 2\tilde{x}^\rho \tilde{x}_\beta
		} \Big/ \pqty{\tilde{y}^8 \tilde{x}^8}\\
		&\xlongequal{\sum_{\mu,\nu}}
		\tilde{y}^{-4} \delta_{\sigma\rho} \pqty{
			\tilde{x}^2\delta^\sigma_\alpha
			- 2\tilde{x}^\sigma \tilde{x}_\alpha
		} \pqty\big{
			\tilde{x}^2\delta^\rho_\beta
			- 2\tilde{x}^\rho \tilde{x}_\beta
		} \Big/ \tilde{x}^8 \\
		&\xlongequal{\sum_{\sigma,\rho}}
			\tilde{y}^{-4} \tilde{x}^{-4}
			\delta_{\alpha\beta}
	\end{aligned}
	\end{gather}
	We see that $g_{\alpha\beta} = f(x)\,\delta_{\alpha\beta}$, with coefficient:
	\begin{equation}
		f(x) = \tilde{y}^{-4} \tilde{x}^{-4}
		\xlongequal{%
			\eqref{eq:special_conformal_decomp}%
		} \frac{x^4}{\tilde{x}^4}
		\xlongequal{%
			\eqref{eq:special_conformal_simplified}%
		} \pqty{
			1 + 2a\cdot x + a^2 x^2
		}^2
	\end{equation}
	\qed[(a)]
	\vspace*{-1\baselineskip}

@@

	In 2D, we have $\mu = z,\bar{z}$; for $\phi(z,\bar{z})$ with conformal weight $(h,\bar{h})$, consider $
		z\mapsto z',\,
		\bar{z}\mapsto \bar{z}'
	$. For convenience, let's first consider a generic variation $\var{z} = \epsilon(z,\bar{z})$ before restricting to spacetime translation; we have:
	\begin{gather}
		\phi'(z',\bar{z}')
		= \pqty\Big{\dv{z'}{z}}^{\!\! -h}
			\pqty\Big{\dv{\bar{z}'}{\bar{z}}}^{
				\!\! -\bar{h}
			}
			\phi(z,\bar{z}),\\[1ex]
		\tilde{\delta}\phi
		= \pqty{
			- h\,\pd\epsilon
			- \bar{h}\,\pdbar\bar{\epsilon}\,
		}\,\phi,\\
		\var{\phi} 
		= \tilde{\delta}\phi
			-\pdv{\phi}{x^\mu} \var{x^\mu}
		= \pqty{
			- h\,\pd\epsilon
			- \bar{h}\,\pdbar\bar{\epsilon}\,
		}\,\phi
			- \epsilon\,\pd\phi
			- \bar{\epsilon}\,\pdbar\phi,
		\label{eq:var_field_compact_supp}
	\end{gather}
	Here we use $\tilde{\delta}\phi$ to denote the ``internal'' variation related to the conformal weights.

	Note that $\phi = b,c$ are anti-commuting Grassmann numbers, variation of the action gives:
	\begin{align}
		\var{S}[b,c,\var{b},\var{c}]
		&= \frac{1}{2\pi} \int \dd[2]{z} \pqty{
			\var{b}\,\pdbar c
			+ b\,\pdbar \var{c}
		} \notag\\
		&= \frac{1}{2\pi} \int \dd[2]{z} \pqty{
			- \pdbar c\,\var{b}
			- \pdbar b\,\var{c}
		} + \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar \pqty{b\var{c}}
		\label{eq:bc_action_var}
	\end{align}
	For \textit{unknown} $b,c$ and {arbitary} $\var{b},\var{c}$, the second term is reduced to a boundary term at infinity and can be dropped; imposing $\var{S} = 0$ gives the equation of motion (EOM): $\pdbar b = \pdbar c = 0$.

	On the other hand, for \textit{on-shell} $b,c$ and compactly supported $\phi = \var{b},\var{c}$ given in \eqref{eq:var_field_compact_supp}, the first term in \eqref{eq:bc_action_var} vanishes while $\var{S}_0 = 0$ still holds; this gives:
	\begin{equation}
	\begin{aligned}
		0 = \var{S}_0
		&= \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar \pqty{b\var{c}}
		= \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar\,\pqty\big{
				- (1-\lambda)\,bc\,\pd\epsilon
				- b\,\pd c\,\epsilon
			} \\
		&= \frac{1}{2\pi} \int \dd[2]{z}
			\pqty\big{
				- (1-\lambda)\,bc\,
					\pdbar\pd\epsilon
				- b\,\pd c\,\pdbar\epsilon
			}
	\end{aligned}
	\end{equation}
	Here we've distributed the $\pdbar$ operator and dropped all terms that vanish automatically by EOM. Next we shall collect the $\pd\epsilon,\pdbar\epsilon$ terms; integrating by parts on the first integrand gives:
	\begin{equation}
	\begin{aligned}
		0 = \var{S}_0
		&= \frac{1}{2\pi} \int \dd[2]{z}
			\pqty\big{
				(1-\lambda)\,\pd(bc)\,
				- b\,\pd c
			}\,\pdbar\epsilon \\
		&= \frac{1}{2\pi} \int \dd[2]{z}
			\pqty\big{
				(\pd b)\,c
				- \lambda\,\pd(bc)
			}\,\pdbar\epsilon \\
		&= - \frac{1}{2\pi} \int \dd[2]{z}
			\epsilon(z,\bar{z})\,\pd_{\bar{z}}
			\pqty\big{
				(\pd b)\,c
				- \lambda\,\pd(bc)
			}
	\end{aligned}
	\label{eq:conserved_current}
	\end{equation}

@@

	To compute $TT$ OPE, we need the OPE of $b(z)\,c(0)$; this is obtained by examining the following path integral, which is zero since the integrand is a total functional derivative:
	\begin{equation}
		0 = \int \mscr{D}b\,\mscr{D}c\,
			\fdv{\phi}\pqty{e^{-S}\,\psi}
	\end{equation}
	Taking $\phi,\psi=b,c$, this generates operator equations such as $
		\pdbar\,b(z)c(0)
		= 2\pi\delta^2(z,\bar{z})
	$. Note that $
		\pdbar(\frac{1}{z})
		= 2\pi\delta^2(z,\bar{z})
	$, which gives:
	\begin{equation}
		b(z)\,c(0) \sim c(z)\,b(0)
		\sim \frac{1}{z},\quad
		b(z)\,b(0) \sim 0
		\sim c(z)\,c(0)
	\end{equation}

@@

	\item[(b)(c)] Combining two $\psi$ expansions gives the mode expansion of $
		J\id{_i^j}
		= \normorder{\psi_i(z)\,\psi^j(z)}
	$, namely:
	\begin{equation}
		J\id{_i^j}(z)
		= \sum_{k\in\mbb{Z}}
			\frac{(J\id{_i^j})_k}{z^{k+1}},\quad
		(J\id{_i^j})_k
		= \sum_{q\in\mbb{Z}+\frac{1}{2}}
			\normorder{
				b_{iq}\,b^{j\dagger}_{k-q}
			}
	\end{equation}
	It is in fact more convenient to obtain the $JJ$ OPE first, and then use it to find the  $[J_0,J_0]$ mode commutator\footnote{
		I would like to thank \textit{谷夏} for providing this hint. 
	}; note that $
		{
			{\psi}_i(z)\,{\psi}^j(w)
		}
	$ contraction gives $\frac{\delta^j_i}{z-w}$, we have:
	\begin{gather}
		J\id{_i^j}(z)\,J\id{_k^l}(0)
		\sim \frac{
			\delta_i^l\delta_k^j
		}{z^2} + \frac{
			\delta^j_k J\id{_i^l}(0)
			- \delta^l_i J\id{_k^j}(0)
		}{z},\\[1ex]
		\bqty{
			(J\id{_i^j})_0, (J\id{_k^l})_0
		}
		= \frac{1}{(2\pi i)^2}
			\oint_0 \dd{w}
			\oint_w \dd{z}
				J\id{_i^j}(z)\,J\id{_k^l}(w)
		= \delta_i^l\,(J\id{_k^j})_0
			- \delta_k^j\,(J\id{_i^l})_0
	\end{gather}

@@

	Similar holds for $J_{ij} = \normorder{\psi_i\psi_j}$ and its OPE, but we no longer need to distinguish upper/lower indices; we have:
	\begin{gather}
		J_{ij}(z)\,J_{kl}(0)
		\sim \frac{
			- \delta_{ik}\delta_{jl}
			+ \delta_{il}\delta_{jk}
		}{z^2} + \frac{
			- \delta_{ik} J_{jl}(0)
			+ \delta_{il} J_{jk}(0)
			+ \delta_{jk} J_{il}(0)
			- \delta_{jl} J_{ik}(0)
		}{z}\\[1ex]
		\bqty{
			(J_{ij})_0, (J_{kl})_0
		}
		= - \delta_{ik} (J_{jl})_0
			+ \delta_{il} (J_{jk})_0
			+ \delta_{jk} (J_{il})_0
			- \delta_{jl} (J_{ik})_0
	\end{gather}
	This is precisely the $\mfrak{o}(n)$ algebra. 
	\qedfull
